Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-20 eswc-2012/phdsymp.tex
ease the hard formulations above benchmarks somewhat
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@108 43ef1190-90fd-4dd7-a769-d0121f02b80e

The above relies on data and queries that are representative of the
system as a whole. It is often asserted that it is not possible to
create a ``one-size-fits-all'' benchmark (see
e.g. \cite{Schmidt:2011:FBS:2063016.2063054}) to cover all aspects of
an application. While that may be true in the general case, I want to
challenge the assumption that a best effort approach is all we can do
in the case of SPARQL (excluding entailment).

@@

Using techniques from statistical experimental design, I propose
that it is possible to design an experiment (i.e. a benchmark) so that
we can prove it covers all realistic cases and with which we can justify
why the remaining corner cases are unlikely to influence the
result. For further elaboration, see Section~\ref{sec:benchmethod}.

>>>>

The above relies on data and queries that are representative of the
system as a whole. It is often asserted that it is not possible to
create a ``one-size-fits-all'' benchmark but answering the above
question requires it.

@@

Using techniques from statistical experimental design, I propose
that it is possible to design an experiment (i.e. a benchmark) which
makes it possible to cover all realistic cases and with which we can justify
why the remaining corner cases are unlikely to influence the
result. For further elaboration, see Section~\ref{sec:benchmethod}.
